A Formal Model of Checked C

### 2023-01-17 sandp23/evaluation.tex
fixing wording in section 6.

\subsection{Dataset}
\input{tables/datasettable}
Network-facing programs such as servers directly interact with external input, often process complex data types, and are more susceptible to security issues.
We primarily focus on network servers as they can benefit most from our partitioning approach.
We use WebAssembly (WASM) as our target sandbox. Consequently, we also want any of the selected programs to be compilable with the WASM sandbox.
We selected network servers that we could (with minimal effort) compile with the WASM compiler.
We also selected a few standalone programs suggested by the ~\checkedc team~\cite{benchmarkcc}, which are good candidates to evaluate modifications to~\checkedc.
The~\tbl{table:dataset} shows the program selected as part of our evaluation dataset.

\subsection{Experimental Setup}
All our experiments are performed on a 6-Core Intel i7-10700H machine with 40 GB of RAM, running Ubuntu 20.04.3 LTS.
We use WASM as our target sandbox and use a similar configuration as that of the recent work~\cite{rlbox-paper}.
We use Valgrind's "massif" memory profiler~\cite{seward2008valgrind} to measure the memory usage and consider the peak heap usage of an application as its memory consumption.
We measure runtime using the difference in elapsed clock cycles using~\code{clock()} API from POSIX's~\code{<time.h>} and linux's ~\code{time} command.
We perform every measurement ten times and use the average as the final result.

@@

\myparagraph{Testbench:}
ProFTPD was evaluated by sampling the time taken to execute its comprehensive test-suite. The delta in run-time between \systemname ProFTPD and its corresponding unconverted version's sample was calculated as a percentage. This percentage was recorded over ten iterations and its median value has been reflected in the table \ref{table:dataset}.

>>>>

\subsection{Dataset}
\input{tables/datasettable}
Network-facing programs such as servers directly interact with external input, often process complex data types, and are more susceptible to security issues.
We primarily focus on network servers as they can benefit most from our partitioning approach.
We use WebAssembly (WASM) as our target sandbox. Consequently, we also want any of the selected programs to be compilable with the WASM sandbox.
We selected network servers that we could (with minimal effort) compile with the WASM compiler.
We also selected a few standalone programs suggested by the ~\checkedc team~\cite{benchmarkcc}, which are good candidates to evaluate modifications to~\checkedc.
\Cref{table:dataset} shows the program selected as part of our evaluation dataset.

\subsection{Experimental Setup}
All experiments are performed on a 6-Core Intel i7-10700H machine with 40 GB of RAM, running Ubuntu 20.04.3 LTS.
We use WASM as our target sandbox and use a similar configuration as that of the recent work~\cite{rlbox-paper};
and Valgrind's "massif" memory profiler~\cite{seward2008valgrind} to measure the memory usage and consider the peak heap usage of an application as its memory consumption.
We measure runtime using the difference in elapsed clock cycles using~\code{clock()} API from POSIX's~\code{<time.h>} and linux's ~\code{time} command, and perform every measurement ten times and use the average as the final result.

@@

\myparagraph{Testbench:}
ProFTPD was evaluated by sampling the time taken to execute its comprehensive test-suite. The delta in run-time between \systemname ProFTPD and its corresponding unconverted version's sample was calculated as a percentage. This percentage was recorded over ten iterations and its median value has been reflected in \Cref{table:dataset}.
